Stack Safety is a Security Property

### 2021-04-13 tex/main.tex

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
%\apt{maybe: ``Stack safety is a testable security property''?}\bcp{That
%  would sacrifice a lot of oomph for a little bit of precision, IMO.  Prefer
%  to leave it out of the title but hit it strongly in the abstract.}%
What is stack safety? The phrase is associated with a variety of compiler,
run-time, and hardware mechanisms for guarding against corruption of stack
memory.  But these mechanisms typically lack rigorous specifications;
they rely instead on informal descriptions of
the safe stack manipulation behaviors that they allow,
or specific examples of the bad behaviors that they prevent.

We propose formal criteria for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state''). We show that our properties describe the behavior of the stack-safety
``micro-policies'' of~\citet{DBLP:conf/sp/RoesslerD18}
using property-based randomized testing. An eager micro-policy
that catches violations immediately enforces our primary ``stepwise''
properties, and we define weaker, more extensional ``observational''
properties that are enforced even by a ``lazy'' micro-policy -- one
that, for performance reasons, may catch violations after they occur
but before they become visible.

These two classes of properties are interesting points along a spectrum
of notions of integrity and confidentiality. The strict stepwise properties can
describe mechanisms that catch errors immediately, the expected behavior of most
enforcement techniques. While the observational properties are closely linked to
lazy micro-policies, they also have the benefit of being highly extensional,
and therefore approaching a plausible minimum specification for stack safety in this
setting.

\apt{This is a good story, but does it describe the paper we are able to produce this week?
  We were rejected before exactly because we claimed to have
  a general criterion, but did not in fact demonstrate its generality (which is not
  obvious). What has changed?}
\sna{It's a delicate line we have to walk, because while our generality may not be
  easily demonstrable, {\em lack} of generality, as BCP pointed out, is also not
  demonstrable. So now I've just taken it out, and I'll plan to talk in the
  introduction about how we hope to be general later.}

  \ifaftersubmission\bcp{should we mention stktokens here?}
  \leo{Not sure. We almost never cite stuff in the abstract, do we?}
  \bcp{Some people say not to, but I think their argument is weak: I've
    added Nick/Andre above.  But I'm not sure we want to get into stkTokens
    in the abstract.}
  \fi
\end{abstract}

@@

\newcommand*{\MemoryLabel}[3]{\raisebox{#2}{\makebox(0,0){\hspace{#1}#3}}}
\newcommand{\memoryaddrs}[1]
  {
    \MemoryLabel{#1}{2em}{\SP}
  }

@@

The call stack is a perennial target for low-level attacks
based on memory-safety vulnerabilities, leading to consequences
that range from leakage or corruption of private stack data to
control-flow hijacking. To detect or prevent such attacks, a profusion of
software and hardware protections have been proposed,
%
including stack canaries~\citep{Cowan+98},
bounds checking~\citep{NagarakatteZMZ09,NagarakatteZMZ10,DeviettiBMZ08},
split stacks~\citep{Kuznetsov+14},
shadow stacks~\citep{Dang+15,Shanbhogue+19},
capabilities~\citep{Woodruff+14,Chisnall+15,Skorstengaard+19,Skorstengaard+19b,Tsampas+19,Georges+21},
and hardware tagging~\citep{DBLP:conf/sp/RoesslerD18}. \ifaftersubmission\apt{Mostly from
  nick; there could be more}\bcp{Yes, going back to MIT days---we should
  include several more of these, if only to give readers the impression that
this is a well-studied mechanism (so formalizing its protections is
useful).}
\fi
%
The protections offered by such mechanisms are generally described in terms
of a set of concrete examples of attacks that they can prevent, such as corruption
of return addresses, buffer overflows, or use of uninitialized variables. This leaves the
task of formulating a more general characterization to the reader's intuition.
Moreover, the details of these mechanisms can be quite intricate
and often involve trading off protection and efficiency.
Thus, it would be useful to have a precise, generic, and formal
specification for stack
safety, both as a basis for comparing the security claims of different
enforcement techniques and for validating more rigorously that these claims
are met by particular implementations.

%\bcp{Does use of unitialized variables lead to stack safety attacks?\apt{sure, via buffer overflow}}
%with the notion usually being
%defined negatively: through examples of stack-based exploits
%\rb{usually though not always; as noted below there are other
%  approaches}\bcp{Yes, we have to be very careful about this}.
%\leo{Examples at a high level}: such as -- does not overwrite return addresses, or ...
The most abstract characterization of which we are aware is in
recent work by \citet{Skorstengaard+19}, which defines stack safety as the conjunction of two
properties:
{\em local state encapsulation (LSE)} and {\em well-bracketed control flow (WBCF)}.
Informally, LSE says that the contents of
a caller's stack frame are not read and written while its callees (and their callees, etc.) are
executing, and WBCF says that callees always
return to the point just after their call (or don't return at all).
\citet{Skorstengaard+19} formalize these properties by defining an idealized machine
in which they visibly hold by construction; an enforcement mechanism (in their case, hardware
capabilities)
can then be shown to provide stack safety by giving a fully abstract embedding function
from the idealized machine to an ordinary machine equipped with the enforcement.
%%
%% While this work represents an important step in the right direction, we believe
%% there is still room to craft an operational characterization
%% of stack safety. \apt{Perhaps our rhetoric should be more micro-policy-specific here?}
%% In other words, we seek formal criteria that can be applied
%% to a mechanism for protecting stack-based low-level programs to judge
%% whether or not it actually ``guarantees stack safety.''
%% \rb{The remainder of this paragraph may be diving too quickly, would a reader be
%% confused by the references to these types of properties, yet to be introduced?}
%% We begin with a strong
%% local state encapsulation property that closely models the behavior of eager
%% micro-policies from \citet{DBLP:conf/sp/RoesslerD18}. This ``eager'' property
%% is too strong to characterize stack safety; reasonable enforcement mechanisms
%% exist that violate it. One such mechanism is a ``lazy'' tag policy, similar to
%% the one in \citet{DBLP:conf/sp/RoesslerD18}. We weaken local state encapsulation
%% to support this technique and argue that the new property, defined relative to an
%% arbitrary notion of observation. This property is still strong enough to prevent
%% the bad behaviors we associate with unsafe stack behavior, but weak enough that
%% other reasonable enforcement mechanisms can enforce it.

In this work, we take the (informal) definition of LSE as a starting
point, but choose a different approach to formalizing it, based on the
technical framework of language-based security~\citep{??}. 
Our core properties are \emph{stepwise stack integrity} and
\emph{stepwise stack confidentiality}.
In applying these security concepts, we treat each caller as needing protection
from its callee, even as that callee may need protection from its callee in turn.
This differs from common practice in language-based security in that the
confidentiality property applies to many nested subtraces within a single execution.
\sna{How novel is this nesting?}
{\em Integrity} says that a caller's local data is protected from modification by its callee,
motivated by the reasoning principle that local data persists across a call. Its
{\em stepwise} interpretation formalizes this very naturally: a caller's local data
is never modified during a call. {\em Confidentiality} says that a caller's data is protected
from being leaked into its callee, and also that the callee cannot see uninitialized data.
As a reasoning principle, confidentiality guarantees that the callee's
behavior is determined only by a predictable interface that does not include the caller's
local state or the uninitialized portion of the stack. This is formalized as a
{\em noninterference}-style property that, rather than comparing pairs of whole program traces,
compares a pair of subtraces for each call, nested within other calls. Once again
{\em stepwise} describes the granularity of enforcement: at every step of a call,
changes in the state are independent of the caller's data.

Together, these properties capture the rough intuition of LSE, but are somewhat stronger.
First, we model returns as returns to a valid return target; an invalid return
is treated as a mere jump within the callee, and does not grant access to the caller's
data. So, even without WBCF, our stack safety properties rule out many control flow attacks.
The attacker in such an instance is permitted to ``return'' so long as it avoids
violating the integrity and confidentiality of the caller. Second, confidentiality
contains temporal protections that LSE does not implicitly address.
\apt{Maybe want to say a little more about this here, since it is a novelty wrt/ existing work?}
\sna{TODO: Say a little more, but make sure it's accurate first.}

One challenge in characterizing stack safety is that in a low-level machine
without built-in stacks, we are at the mercy of architectural
choices that do not relate to the abstract notion of stack safety. Some implementations
may have only a stack pointer while others add a frame pointer, in some systems return
addresses and data live in separate stacks, and so on. We abstract over these choices
as much as possible, so that our model can be applied to a wide range of architectures
and enforcement mechanisms.

@@

To illustrate the applicability of these properties, we perform randomized testing to
validate that \citeauthor{DBLP:conf/sp/RoesslerD18}'s Depth Isolation micro-policy enforces
them. Randomized testing is a relatively low-cost way to validate a potential enforcement
mechanism; it finds flaws in the enforcement fast enough to be integrated into the workflow
of enforcement development \citep{TestingNI:ICFP}. To demonstrate that the testing adequately
covers potentially erroneous programs, we test intentionally buggy policies alongside
the real one. If the testing can differentiate correct implementations from buggy ones,
it is an argument in favor of their correctness.
%\apt{more to say?}\bcp{Yes---partly to underscore our claim that this is a
%  significant contribution, and partly to give the reader some context for
%  why this is part of our story.  E.g., ``One nice thing we can do with our
%  spec is to use it to evaluate the claims of existing or future proposals
%  for enforcement mechanisms.  One relatively inexpensive way to carry out
%  such an evaluation is to see whether property-based testing against this
%  spec can distinguish correct implementations of the mechanism from buggy
%  ones...''}
Of course, as our testing reveals, \citeauthor{DBLP:conf/sp/RoesslerD18}'s Lazy Tagging and
Clearing micro-policy does not enforce stepwise integrity.
Unfortunately the existing Lazy Tagging and Clearing
micro-policy does not quite enforce observable confidentiality either. %, as we show in
%testing~\apt{really??},
But formalizing the ideal property allows us to see how it falls short -- a specific
violation of the temporal aspect of confidentiality.
We propose  a variant of Lazy Tagging and Clearing that we believe \emph{does} enforce
observational integrity, at some performance cost.\apt{but we're not testing that, right?}
\rb{Not sure about the property part right now, the machine side of this is
  pretty much done}
\sna{It's aspirational so far, but there's no fundamental reason we can't test it. We may
  need a caveat about how it's harder to test?}\apt{As per email discussion,
  maybe we could have a property variant that \emph{does} match depth-based Lazy Tagging and Clearing,
  by loosening the temporal safety properties?}

Our initial description of these properties assumes a single simple stack with no sharing between callers and
callees: all parameters and return values are passed in registers.  However,
we can refine it to allow passing of scalar stack data, granting a callee
access to the caller's data. (We do not model more sophisticated sharing, because to do
so realistically would require a separate protection scheme, such as a capability
model.\bcp{This is all a bit mysterious} While this is quite feasible in a tag-based enforcement mechanism, it is properly
a separate policy outside the scope of stack safety. A tag-based approach can easily
compose multiple such policies.)
\rb{So no pointer passing? Pass by reference is now discussed at the end of
  Section 3, however it looks like things get tricky rather quickly.}
\sna{The trick is that if a programmer is passing pointers, we can't presume their
  intent -- how long should we permit memory to be shared? But if the compiler is passing
  pointers, as in pass by reference, we have a clear sense of where sharing should stop.
  \apt{N.B.Doing pass-by-reference properly requires that the passed variable is accessible
    by all descendents, not just immediate callee, which is doable with depth tags but not
    obviously with per-activation tags }}

Finally, we define integrity and confidentiality properties for a coroutine system featuring
finitely-bounded stacks.
Though simplistic, this extension is a step toward concurrency and demonstrates that
our approach is flexible enough to handle more sophisticated styles of
control flow.

@@

In summary, we offer the following contributions: \bcp{Section numbers are
  wonky---why just 7.1, where is 8, etc.}
\begin{itemize}
\item
  We adapt formulations of integrity and confidentiality from language-based security
  to formalize a parameterized {\em stepwise stack-safety} property and argue that it
  captures the intuitive concepts of stack safety~(\cref{sec:lse}). Our model extends to
  argument passing on the stack and to a simple coroutine system.
\item
  We use a property-based randomized testing framework to support the claim
  that this stepwise property is actually enforced by the Depth Isolation policy
  of~\citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:testing}).
\item
  We formalize a weaker but more extensional \emph{observational} variant of the
  stack safety property and argue that it accurately characterizes
  the Lazy Tagging and Clearing policy of~\citet{DBLP:conf/sp/RoesslerD18}
  enhanced with unique tags on each activation~(\cref{sec:lazy}).
\end{itemize}

@@

Our examples are written in C-like syntax, labeled with line numbers for reference,
but to reflect the increased power of the underlying assembly code, we allow code
to read the stack pointer ({\tt \$SP}) directly and use
it to form pointers.\apt{I've added some strategic *'s}
Call and return annotations are marked {\tt[C]} and {\tt[R]}
respectively. Local variables are assumed to be stored in the stack frame,
in declaration order. Unless otherwise stated, arguments and return values are passed in registers.
The machine is word-addressed. The stack grows upward in
memory and {\tt \$SP} points to the first unused word above the top of the stack. 
At the right of each example, we show the layout of stack memory just before
the specified line number is executed; each box represents a memory word and
addresses increase to the right.

@@

This form of confidentiality we will term {\em lockstep confidentiality}, defined informally
as: for any state at the entry to a function, for any variant over the values in the stack,
the primary state and its variant will step in lockstep until they return. Any system components\apt{first use of this?}
whose values change will be identical between the primary and variant traces. This includes not
just memory, but registers as well, so that returning a secret is a violation. And when we
extend the model with a notion of external output, it\apt{what?}  will include any values that
emitted.

We alternatively could imagine a stepwise form of confidentiality in which we explicitly
track which addresses may be read (i.e., which have been initialized), and at each step
guarantee that the step alters state identically to a step from a variant state. Then we
wouldn't need to divide up the execution by calls. But we can see in this example that taking
a single variant at the start of the call effectively captures initialization: when {\tt y} is
initialized, the primary and the variant agree on its value, so it can now be safely read.
This treatment is roughly in line with more standard uses of noninterference, which typically
vary states at the starts of whole program runs.\apt{This is all a bit cryptic.}

Together, stepwise integrity and lockstep confidentiality form the stepwise version of
local state encapsulation.

@@

\sna{Not terribly happy with the circles yet; the idea is that instead of a meta-level
  label for the line numbers we could treat the PC as a part of the system we're showing.}

\paragraph*{Control Flow Attacks}
\begin{figure}
  \centering
  \begin{minipage}{.4\textwidth}
\begin{verbatim}
int *stash = 0;

@@

void f() {
10:     if(!stash) {
        // store return pointer
11:       stash = $SP-1;
12:     } else {
13:       $SP-1 = stash;
14:       stash = 0;
        }
15[R]:    return;
}
\end{verbatim}
  \end{minipage}
\label{fig:controlflow}
 %  \begin{subfigure}[t]{.4\textwidth}
 %\begin{verbatim}
 %int counter = 0;
@@ -1194,42 +1090,43 @@ the program counters will differ, breaking the lockstep.
 %\end{verbatim}
 %\label{fig:WBCF2}
 %  \end{subfigure}
-%  \caption{Control Flow Attacks}
-%  \label{fig:WBCF}
-%\end{figure}
+  \caption{Control Flow Attacks}
+  \label{fig:WBCF}
+\end{figure}

@@

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
%\apt{maybe: ``Stack safety is a testable security property''?}\bcp{That
%  would sacrifice a lot of oomph for a little bit of precision, IMO.  Prefer
%  to leave it out of the title but hit it strongly in the abstract.}%
What is stack safety? The phrase is associated with a variety of compiler,
run-time, and hardware mechanisms for guarding against corruption of stack
memory.  But these mechanisms typically lack rigorous specifications,
relying instead on informal descriptions of
the safe stack manipulation behaviors that they allow
and/or specific examples of the bad behaviors that they prevent.

We propose formal criteria for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state'').
% These properties are sensible even in the presence of
% abnormal control flow.\apt{Is this important enough to mention here?}
% BCP: I think not in the abstract, but maybe in the intro.
% We further apply\apt{what does this mean? we didn't
%  invent it} a straightforward notion of
% ``well-bracketed control flow'' that restricts control flow to the
% typical pattern of matched calls and returns.
%
We argue that these criteria match common intuitions (1) by showing that
they are violated by a variety of intuitively unsafe examples and (2) by
using property-based random testing to check that appropriate variants of
the criteria are actually enforced by the stack-safety ``micro-policies''
proposed by~\citet{DBLP:conf/sp/RoesslerD18} (and {\em not} enforced by
broken versions of these enforcement mechanisms).  Specifically, Roessler
and Dehon's ``eager'' micro-policy, which catches violations as early as
possible, enforces the basic ``stepwise'' versions of our confidentiality
and integrity properties. Their more performant ``lazy'' micro-policy
does not, but inspires weaker, more extensional ``observational'' variants of the
properties. While we do not rule out other enforcement mechanisms, our
definitions are strongly informed by micropolicy systems, especially our
notion of observational integrity.
\sna{Seems like the best place to admit we're tied to micropolicies is
  while discussing micropolicies.}

\bcp{We should mention stack data and coroutines, I think?  Maybe in the
  context of an expectation-lowering hedge, like:}%
For the sake of concreteness, most of our presentation assumes a RISC-V
machine architecture with a basic subroutine calling convention, where
parameters are passed in registers. We also show how to accomodate
stack-allocated parameter passing and coroutines.

\bcp{this is also a
  good place to admit that our definitions are tuned for micropolicies, if
  we can find a succinct way to say it.}
\sna{See above.}

% We argue \apt{do we?}\bcp{I guess we will not have time to.  Propose
%   deleting this para.} that our properties are suited to a range of other
% enforcement mechanisms. The strict stepwise properties can describe
% mechanisms that catch errors immediately, as is typical. While the
% observational properties are closely linked to lazy micro-policies they are
% weak enough to be a lower bound that captures stack safety for any
% reasonable enforcement mechanism.

\apt{This is a good story, but does it describe the paper we are able to produce this week?
  We were rejected before exactly because we claimed to have
  a general criterion, but did not in fact demonstrate its generality (which is not
  obvious). What has changed?}\bcp{I agree with these concerns. Deleted the
  para about the general story.  Does the rest now avoid making (or
  implying) claims that we can't defend?}
\bcp{Also, I think we should save
  WBCF for the intro---I can't find a way to discuss it here that is brief
  and not confusing/distracting.}

  % \ifaftersubmission\bcp{should we mention stktokens here?}
  % \leo{Not sure. We almost never cite stuff in the abstract, do we?}
  % \bcp{Some people say not to, but I think their argument is weak: I've
  %   added Nick/Andre above.  But I'm not sure we want to get into stkTokens
  %   in the abstract.}
  % \fi
\end{abstract}

@@

\newcommand*{\MemoryLabel}[3]{\raisebox{#2}{\makebox(0,0){\hspace{#1}#3}}}
\newcommand{\memoryaddrs}[2][]
  {
    \MemoryLabel{#2}{2em}{\SP #1}
  }

@@

The call stack is a perennial target for low-level attacks
based on memory-safety vulnerabilities, leading to consequences
that range from leakage or corruption of private stack data to
control-flow hijacking. To deter or detect such attacks, a profusion of
software and hardware protections have been proposed,
%
including stack canaries~\citep{Cowan+98},
bounds checking~\citep{NagarakatteZMZ09,NagarakatteZMZ10,DeviettiBMZ08},
split stacks~\citep{Kuznetsov+14},
shadow stacks~\citep{Dang+15,Shanbhogue+19},
capabilities~\citep{Woodruff+14,Chisnall+15,Skorstengaard+19,Skorstengaard+19b,Tsampas+19,Georges+21},
and hardware tagging~\citep{DBLP:conf/sp/RoesslerD18}. \ifaftersubmission\apt{Mostly from
  nick; there could be more}\bcp{Yes, going back to MIT days---we should
  include several more of these, if only to give readers the impression that
this is a well-studied mechanism (so formalizing its protections is
useful).}
\fi
%
The protections offered by such mechanisms are commonly described in terms
of concrete examples of attacks that they can prevent, such as corruption
of return addresses, buffer overflows, or use of uninitialized variables,
leaving a more abstract characterization to the reader's intuition.
But these mechanisms can be quite intricate
and often require trading off protection and efficiency.
Thus, it would be useful to have a precise, generic, and formal
specification for stack
safety, both as a basis for comparing the security claims of different
enforcement techniques and for validating more rigorously that these claims
are met by particular implementations.

%\bcp{Does use of unitialized variables lead to stack safety attacks?\apt{sure, via buffer overflow}}
%with the notion usually being
%defined negatively: through examples of stack-based exploits
%\rb{usually though not always; as noted below there are other
%  approaches}\bcp{Yes, we have to be very careful about this}.
%\leo{Examples at a high level}: such as -- does not overwrite return addresses, or ...
The most abstract characterization stack safety of which we are aware is in
recent work by \citet{Skorstengaard+19}, which defines stack safety as the conjunction of two
properties:
{\em local state encapsulation (LSE)} and {\em well-bracketed control flow (WBCF)}.
Informally, LSE says that the contents of
a caller's stack frame are not read and written while its callees (and their callees, etc.) are
executing, and WBCF says that callees always
return to the point just after their call (if they return at all).
\citet{Skorstengaard+19} formalize these properties by defining an idealized
machine in which they hold {\em by construction}; an enforcement mechanism (in their case, hardware
capabilities)
can then be shown to guarantee stack safety by exhibiting a fully abstract
embedding function
from the idealized machine to an ordinary machine equipped with this
enforcement mechanism.  \bcp{Many OOPSLA readers/reviewers will not
  understand that sentence.}
%%
%% While this work represents an important step in the right direction, we believe
%% there is still room to craft an operational characterization
%% of stack safety. \apt{Perhaps our rhetoric should be more micro-policy-specific here?}
%% In other words, we seek formal criteria that can be applied
%% to a mechanism for protecting stack-based low-level programs to judge
%% whether or not it actually ``guarantees stack safety.''
%% \rb{The remainder of this paragraph may be diving too quickly, would a reader be
%% confused by the references to these types of properties, yet to be introduced?}
%% We begin with a strong
%% local state encapsulation property that closely models the behavior of eager
%% micro-policies from \citet{DBLP:conf/sp/RoesslerD18}. This ``eager'' property
%% is too strong to characterize stack safety; reasonable enforcement mechanisms
%% exist that violate it. One such mechanism is a ``lazy'' tag policy, similar to
%% the one in \citet{DBLP:conf/sp/RoesslerD18}. We weaken local state encapsulation
%% to support this technique and argue that the new property, defined relative to an
%% arbitrary notion of observation. This property is still strong enough to prevent
%% the bad behaviors we associate with unsafe stack behavior, but weak enough that
%% other reasonable enforcement mechanisms can enforce it.

In this work, we also distinguish between protecting data (like LSE) and
control flow (with WBCF), and formalize a data protection property
based on the technical framework of language-based security~\citep{??}.
Our core properties are \emph{stepwise stack integrity} and
\emph{stepwise stack confidentiality}. WBCF is a desireable property, but
we can express safety in an information-flow sense without reference to it,
even safety from attacks that hijack control flow.

In applying these security concepts, we treat each caller as needing protection
from its callee, even as that callee may need protection from its callee in turn.
This differs from common practice in language-based security in that the
confidentiality property applies to many nested subtraces within a single execution.
\sna{How novel is this nesting?}
{\em Integrity} says that a caller's local data is protected from modification by its callee,
motivated by the reasoning principle that local data persists across a call. Its
{\em stepwise} interpretation formalizes this very naturally: a caller's local data
is never modified during a call. {\em Confidentiality} says that a caller's data is protected
from being leaked into its callee, and also that the callee cannot see uninitialized data.
As a reasoning principle, confidentiality guarantees that the callee's
behavior is determined only by a predictable interface that does not include the caller's
local state or the uninitialized portion of the stack. This is formalized as a
{\em noninterference}-style property that, rather than comparing pairs of whole program traces,
compares a pair of subtraces for each call, nested within other calls. Once again
{\em stepwise} describes the granularity of enforcement: at every step of a call,
changes in the state are independent of the caller's data.

Together, these properties capture the rough intuition of LSE, but are somewhat stronger.
First, we model returns as returns to a valid return target; an invalid return
is treated as a mere jump within the callee, and does not grant access to the caller's
data. So, even without WBCF, our stack safety properties rule out many control flow attacks.
The attacker in such an instance is permitted to ``return'' so long as it avoids
violating the integrity and confidentiality of the caller. Second, confidentiality
contains temporal protections that LSE does not implicitly address.
\apt{Maybe want to say a little more about this here, since it is a novelty wrt/ existing work?}
\bcp{+1}\sna{TODO: Say a little more, but make sure it's accurate first.}

One challenge in characterizing stack safety formally is that in a low-level machine
without built-in stacks, we are at the mercy of architectural
choices that do not relate to the abstract notion of stack safety. Some implementations
may have only a stack pointer while others add a frame pointer, in some systems return
addresses and data live in separate stacks, and so on. We abstract over these choices
as much as possible.

@@

\bcp{This paragraph doesn't apply to the lazy properties, so maybe it should
be moved before they are introduced?}%
To illustrate the applicability of these properties, we perform randomized testing to
validate that \citeauthor{DBLP:conf/sp/RoesslerD18}'s Depth Isolation micro-policy enforces
them. Randomized testing is a relatively low-cost way to validate a potential enforcement
mechanism; it finds flaws in the enforcement fast enough to be integrated into the workflow
of enforcement development \citep{TestingNI:ICFP}. To demonstrate that the testing adequately
covers potentially erroneous programs, we test intentionally buggy policies alongside
the real one. If the testing can differentiate correct implementations from buggy ones,
it is an argument in favor of their correctness. \bcp{Hmm--don't understand
  that sentence}
%\apt{more to say?}\bcp{Yes---partly to underscore our claim that this is a
%  significant contribution, and partly to give the reader some context for
%  why this is part of our story.  E.g., ``One nice thing we can do with our
%  spec is to use it to evaluate the claims of existing or future proposals
%  for enforcement mechanisms.  One relatively inexpensive way to carry out
%  such an evaluation is to see whether property-based testing against this
%  spec can distinguish correct implementations of the mechanism from buggy
%  ones...''}
Of course, as our testing reveals, \citeauthor{DBLP:conf/sp/RoesslerD18}'s Lazy Tagging and
Clearing micro-policy does not enforce stepwise integrity.
Unfortunately the existing Lazy Tagging and Clearing
micro-policy does not quite enforce observable confidentiality either. %, as we show in
%testing~\apt{really??},
But formalizing the ideal property allows us to see how it falls short -- a specific
violation of the temporal aspect of confidentiality.
We propose  a variant of Lazy Tagging and Clearing that we believe \emph{does} enforce
observational integrity, at some performance cost.\apt{but we're not testing that, right?}
\rb{Not sure about the property part right now, the machine side of this is
  pretty much done}
\sna{It's aspirational so far, but there's no fundamental reason we can't test it. We may
  need a caveat about how it's harder to test?}\apt{As per email discussion,
  maybe we could have a property variant that \emph{does} match depth-based Lazy Tagging and
  Clearing, by loosening the temporal safety properties?}
\sna{I'm pretty sure for the main policy it's just lazy integrity, no confidentiality.
  There was a variant Nick and Andre gave that would restrict the leaks to only be between
  instances of the same function, so that's the same property under a weaker attacker model,
  where we don't protect a function from itself.}

Our initial description of these properties assumes a single simple stack with no sharing
between callers and callees: all parameters and return values are passed in registers.  Later,
we show how to refine it to allow passing of scalar stack data, granting a
callee access to the caller's data. We do not model more sophisticated sharing,
such as taking the address of a variable and treating it like a pointer. Doing so without
protecting the variable is not interesting, and protecting would be better suited to
a different kind of enforcement, such as a memory safety micro-policy or Cheri-style capability.
\bcp{This is all a bit mysterious} \sna{Any less mysterious now?}

\rb{So no pointer passing? Pass by reference is now discussed at the end of
  Section 3, however it looks like things get tricky rather quickly.}
\sna{The trick is that if a programmer is passing pointers, we can't presume their
  intent -- how long should we permit memory to be shared? But if the compiler is passing
  pointers, as in pass by reference, we have a clear sense of where sharing should stop.
  \apt{N.B.Doing pass-by-reference properly requires that the passed variable is accessible
    by all descendents, not just immediate callee, which is doable with depth tags but not
    obviously with per-activation tags }}

Finally, we define integrity and confidentiality properties for a coroutine system featuring
a static layout, in which each coroutine's stack is constrained to a fixed region of memory.
Though simplistic, this extension is a step toward concurrency and demonstrates that
our approach is flexible enough to handle more sophisticated styles of
control flow.

@@

In summary, we offer the following contributions:
\begin{itemize}
\item
  We adapt formulations of integrity and confidentiality from language-based security
  to formalize a parameterized {\em stepwise stack-safety} property and argue that it
  captures the intuitive concepts of stack safety~(\cref{sec:lse}). Our model extends to
  argument passing on the stack and to a simple coroutine system.
\item
  We use a property-based randomized testing framework to support the claim
  that this stepwise property is actually enforced by the Depth Isolation policy
  of~\citet{DBLP:conf/sp/RoesslerD18}~(\cref{sec:testing}).
\item
  We formalize a weaker but more extensional \emph{observational} variant of the
  stack safety property and argue that it accurately characterizes
  the Lazy Tagging and Clearing policy of~\citet{DBLP:conf/sp/RoesslerD18}
  enhanced with unique tags on each activation~(\cref{sec:lazy}).
\end{itemize}

@@

Our examples are written in C-like syntax, labeled with line numbers for reference,
but to reflect the increased power of the underlying assembly code, we allow code
to read the stack pointer ({\tt \$SP}) directly and use
it to form pointers.
Call and return annotations are marked {\tt[C]} and {\tt[R]}
respectively. Local variables are assumed to be stored in the stack frame,
in declaration order. Unless otherwise stated, arguments and return values are passed in registers.
The machine is word-addressed. The stack grows upward in
memory and {\tt \$SP} points to the first unused word above the top of the stack.
At the right of each example, we show the layout of stack memory just before
the specified line number is executed; each box represents a memory word and
addresses increase to the right.

@@

This form of confidentiality we will term {\em stepwise confidentiality}, defined informally
as: for any state at the entry to a function, for any variant over the values in the stack,
the primary state and its variant will step in lockstep until they return. To step in lockstep
means that if both states step -- that is, neither the primary nor the variant failstops --
any {\em system component} (such as memory cell, register, program counter) that changes
in one step has a matching value at the end of the other step. And when we
extend the model with a notion of external output, values that are outputted will need
to match as well.

We alternatively could imagine a version of stepwise confidentiality in which we explicitly
track which addresses may be read (i.e., which have been initialized), and at each step
guarantee that the step alters state identically to a step from a variant state. Then we
wouldn't need to divide up the execution by calls. But the approach we take is more
consistent with a typical noninterference approach, in that it varies the memory once
at the beginning and trace changes through the execution.

@@

\paragraph*{Control Flow Attacks}
\begin{figure}
  \centering
  \begin{subfigure}{.4\textwidth}
\begin{verbatim}
int *stash = 0;

@@

void f() {
10:     if(!stash) {
        // store return pointer
11:       stash = $SP-1;
12:     } else {
13:       *($SP-1) = stash;
14:       stash = 0;
        }
15[R]:    return;
}
\end{verbatim}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \begin{tabular}{l l l}
      {\tt 2} &
      \memoryaddrs{8em}
      \memory{4}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-19em}{0.75em}{1} \\
      {\tt 15} &
      \memoryaddrs{12em}
      \memory{1}{\mainsealc}[Seal(0)]%
      \memory{1}{\goodc}[RetPtr]%
      \memory{2}{\unsealc}%
      ~$\cdots$
      \MemoryLabel{-19em}{0.75em}{1}
      \MemoryLabel{-15em}{0.75em}{3}
      \vspace{.5em} &
      \memory[3em]{1}{\mainsealc}[Target]%
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = 3}
      \\
      {\tt 3} &
      \memoryaddrs{8em}
      \memory{4}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-19em}{0.75em}{1} \\
      {\tt 10} &
      \memoryaddrs{12em}
      \memory{1}{\mainsealc}
      \memory{1}{\goodc}
      \memory{2}{\unsealc}%
      ~$\cdots$
      \MemoryLabel{-19em}{0.75em}{-1}
      \MemoryLabel{-15em}{0.75em}{5} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = 5}
      \\
      {\tt 15} &
      \memoryaddrs{12em}
      \memory{1}{\mainsealc}
      \memory{1}{\badc}
      \memory{2}{\unsealc}%
      ~$\cdots$
      \MemoryLabel{-19em}{0.75em}{-1}
      \MemoryLabel{-15em}{0.75em}{3} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = 5}
      \\
      {\tt 3} &
      \memoryaddrs{8em}
      \memory{1}{\mainsealc}
      \memory{3}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-19em}{0.75em}{-1} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = 5}
      \\
      {\tt 4} &
      \memoryaddrs{8em}
      \memory{1}{\mainsealc}
      \memory{3}{\unsealc}
      ~$\cdots$
      \MemoryLabel{-19em}{0.75em}{\bf 1} &
      \memory[3em]{1}{\mainsealc}
      \MemoryLabel{-3em}{0.75em}{\(\PCname\) = 5} \\
    \end{tabular}
  \end{subfigure}
  \label{fig:controlflow}
  \caption{A Control Flow Attack}
\end{figure}

From the classic stack smashing attack to return oriented programming, 
one of the most pernicious ways to attack the stack is by hijacking control flow.
Our stack safety properties do not assume that control flow is well-bracketed; rather,
they express what it means to protect data even in the presence of control-flow attacks.
Consider example \ref{fig:controlflow}, a relative of the classic ``awkward example,''
in which {\tt f} is called twice, at lines 2 and 4. It should therefore return to lines
3 and 5, respectively. But the first time, before returning, it stashes its
return pointer away, and the second time it returns to line 3 instead of 5; then it ends
up called a third time, at which point it returns to line 5.

Reasoning about {\tt main}, we expect that {\tt x} is negated once, so that we return
-1. But because of {\tt f}'s interference, we negate {\tt x} twice, and return 1.
This has the appearance of an integrity violation. But how can that be?

The key intuition is that to return to {\tt main}, {\tt f} needs to do more than just
execute a return-labeled instruction. It must then actually reach the appropriate
{\em return target} in {\tt main}. In our context, we keep a stack of return targets,
which correspond to the depths at which stack frames have been sealed. A callee is
only considered to have returned when it executes a return-annotated instruction
and then reaches a valid return target. Only then do the sealed frames become unsealed.

In the example, on its first return, {\tt f} reaches its return target, because the
\(\PCname\) is 3 after its return. But on the second, {\tt f} does not properly return,
but rather changes its stack pointer and jumps into {\tt main}'s code. Then {\tt f}
attempts to overwrite the sealed value of {\tt x}, violating integrity.

@@

\begin{figure}
  \centering
  \begin{subfigure}{.3\textwidth}
\begin{verbatim}
int main() {
0:           int x;
1:           x = 5;
2[P($SP)C]:  x = f(x);
3[R]:        return x;
}
